Papers

### 2025-05-28 papers.qmd
update paper info

- McKay B., Bacelar MFB., Parma JO., Miller MW., & Carter MJ. (In Press). The combination of reporting bias and underpowered study designs has substantially exaggerated the motor learning benefits of self-controlled practice and enhanced expectancies: A meta-analysis. *International Review of Sport and Exercise Psychology*. ---
[{{< ai doi >}}](https://doi.org/10.1080/1750984X.2023.2207255){target="_blank" style="color: inherit;"}
[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2023_mckay-etal_the-combination-of-reporting-bias-and-underpowered-study-designs-has-substantially-exaggerated-the-motor-learning-benefits-of.pdf){target="_blank" style="color: inherit;"}
[{{< fa brands github >}}](https://github.com/cartermaclab/proj_sc-ee-optimal-theory){target="_blank" style="color: inherit;"}

@@

>>>>

@@

- McKay B., Bacelar MFB., Parma JO., Miller MW., & Carter MJ. (2025). The combination of reporting bias and underpowered study designs has substantially exaggerated the motor learning benefits of self-controlled practice and enhanced expectancies: A meta-analysis. *International Review of Sport and Exercise Psychology*. ---
[{{< ai doi >}}](https://doi.org/10.1080/1750984X.2023.2207255){target="_blank" style="color: inherit;"}
[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2025_mckay-etal_the-combination-of-reporting-bias-and-underpowered-study-designs-has-substantially-exaggerated-the-motor-learning-benefits-of.pdf){target="_blank" style="color: inherit;"}
[{{< fa brands github >}}](https://github.com/cartermaclab/proj_sc-ee-optimal-theory){target="_blank" style="color: inherit;"}
